The use of lithic assemblages for the definition of short-term occupations in hunter-gatherer prehistory

### 2018-04-15 analysis/paper/paper.Rmd
1st version

#library(ShortTermOccupations) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
```

>>>>

library(ShortTermOccupations) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
```
